---
name: Benjamin Andrew Keisling
position: Postdoctoral Research Scientist, LDEO
address: "109 Oceanography, 61 Route 9W, Palisades, NY 10964"
www: benjaminkeisling.weebly.com/
email: "keisling@lamont.columbia.edu"
twitter: palaeobak
github: bkeisling
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::hyndman
headcolor: "000088"
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tidyverse)
library(lubridate)
library(here)
```

```{r presentations, include=FALSE}
presentations.raw <- read_csv(here::here("data", "presentations.csv"))
presentations <- 
  presentations.raw %>% 
  mutate(When = mdy(When))
```


# Research Interests
* ice-sheet stability, ice-sheet mass balance, climate and ice-sheet models, ice-ocean interactions, climatic thresholds, Pliocene-Pleistocene transition, mechanisms underlying Pleistocene glacial/interglacial diversity

# Teaching Interests
* glaciology, glacial geology, paleoclimatology, physical oceanography, climatology, paleoceanography

# Appointments

```{r}
tribble(
  ~ uni, ~ loc, ~ degree, ~ dates,
  "Lamont-Doherty Earth Observatory", "Palisades, NY", "Postdoctoral Fellow", "Jan. 2020 - present"
) %>% 
  detailed_entries(degree, loc, uni, dates)
```


# Education

```{r}
tribble(
  ~ uni, ~ loc, ~ degree, ~ dates,
  "University of Massachusetts Amherst", "Amherst, MA", "Ph.D. Geosciences", "Sept. 2015 - Oct. 2019, conferral date 02/01/2020", 
    "Niels Bohr Institute, University of Copenhagen", "Copenhagen, DK", "Visiting Fellow, Centre of Ice and Climate", "Aug. 2016 - June 2017", 
  "University of Massachusetts Amherst", "Amherst, MA", "M.Sc. Geosciences", "Sept. 2013 - May 2015", 
  "Saint Olaf College", "Northfield, MN", "B.A. Physics", "Sept. 2009 - May 2013"
) %>% 
  detailed_entries(degree, loc, uni, dates)
```

# Fellowships, Grants and Awards

```{r}
read_csv(here::here("data", "awards-and-grants.csv")) %>% 
  mutate(year = str_extract(date, "\\d{4}")) %>% 
  arrange(desc(year)) %>% 
  detailed_entries(what = award, when = date)
```

# Publications

```{r research-papers}
# Normal articles excluding editorials
bibliography_entries("../data/bakpubs.bib") %>%
#  transform(year=as.numeric(year)) %>%
  arrange(year)
```

# Invited Guest Lectures

```{r}
presentations %>% 
  filter(Tag == "lecture") %>% 
  arrange(desc(When)) %>% 
  detailed_entries(what = Title, when = glue("{month(When, label = TRUE)} {year(When)}"), where = paste(Location,Award,sep=" host: "))
```

# Teaching

```{r}
tribble(
  ~ loc, ~ title, ~ dates,
  "UMass Amherst", "Instructor of Record, CNS 191, Adapting to a Dynamic Environment", "2015" 
) %>% 
  detailed_entries(where=loc, what=title, when = dates)
```

# Fieldwork

```{r}
tribble(
  ~ loc, ~ title, ~ dates,
  "Ross Sea, West Antarctica", "(8 weeks) Shipboard Sedimentologist, International Ocean Discovery Program (IODP) Expedition 374", "2018",
    "EGRIP, Northeast Greenland", "(3 weeks) Member of field team at EGRIP ice core drill site in NE Greenland", "2017",
  "Basin Pond, ME", "Limnogeology research at Basin Pond", "2014-2019",
  "Svartisen Subglacial Laboratory", "Glaciology research at Engabreen Glacier, Arctic Norway", "2012"
) %>% 
  detailed_entries(where=loc, what=title, when = dates)
```

# Summer Schools / Courses

```{r}
tribble(
  ~ loc, ~ title, ~ dates,
  "Yosemite, CA", "Advanced Climate Dynamics Course", "2019",
  "Copenhagen, DK", "Ice Core Analysis Techniques", "2016",
  "McCarthy, AK", "International Glaciology Summer School", "2016",
  "Minneapolis, MN", "Expert Witness Training Academy", "2016",
  "Urbino, IT", "USSSP", "2014"

) %>% 
  detailed_entries(where=loc, what=title, when = dates)
```

# Pending Collaborative Grants/Proposals

```{r}
tribble(
  ~ loc, ~ title, ~ dates,
  "Submitted to NSF, PIs: Schaefer, Briner, DeConto, Anandakrishnan", "Collaborator, Greendrill Project", "2019",
  "IODP Proposal 814_Full_2 to drill Eirik Drift and Davis Strait in 2022", "Proponent", "2018",
  "IODP Proposal 909_Full_2 to drill Melville Bugt and Baffin Bay in 2022", "Proponent", "2018",
  "Named Collaborator, RAFTS Proposal submitted to NERC (UK)", "Lead PI: Tina Van de Flierdt", "not funded, 2018",
  "Named Collaborator, ANTIPODES Proposal submitted to PNRA (IT)", "Lead PI: Florence Colleoni", "funded, 2018"
) %>% 
  detailed_entries(where=loc, what=title, when = dates)
```

# Outreach and Service

```{r}
read_csv(here::here("data", "outreach-and-service.csv")) %>% 
  mutate(year = str_extract(date, "\\d{4}")) %>% 
  arrange(desc(year)) %>% 
  detailed_entries(what = award, when = date, with = where, why=details)
```



# Presentations

## Talks

```{r}
presentations %>% 
  filter(Tag == "oral") %>% 
  arrange(desc(When)) %>% 
  detailed_entries(what = Title,
                   when = glue("{month(When, label = TRUE)} {year(When)}"),
                   with = Authors,
                   where = paste(Conference, Location, sep=", "),
                   why = Award)
```

## Posters

```{r}
presentations %>% 
  filter(Tag == "poster") %>% 
  arrange(desc(When)) %>% 
  detailed_entries(what = Title,
                   when = glue("{month(When, label = TRUE)} {year(When)}"),
                   with = Authors,
                   where = paste(Conference, Location, sep=", "),
                   why = Award)
```



# Misc